%%
%% Author: pharrell_wang
%% 13/10/2017
%%

% Preamble
\documentclass[11pt,twoside,a4paper]{article}

% Packages
\usepackage{a4wide}
\usepackage{verbatim} % for block comment
\usepackage{color}   % May be necessary if you want to color links
\usepackage{hyperref}
\usepackage{textcomp}
\hypersetup{
colorlinks=true, %set true if you want colored links
linktoc=all,     %set to all if you want both sections and subsections linked
linkcolor=black,  %choose some color if you want links to stand out
}

\usepackage[margin=1in,headheight=13.6pt]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
%\chead{This is the page header}
%\cfoot{Page \thepage}
% define the title
\author{Zhen-Xiang WANG}
\title{\LaTeX{} Practice}

% Document
\begin{document}
    \thispagestyle{empty}
    \maketitle
    \tableofcontents

    \section{This is my first section}\label{sec:thisIsMyFirstSection}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \Large Not shelfful\\
    but shelf\mbox{}ful

    \ldots (low dots)\\
    Not like this ... but like this:\\
    New York, Tokyo, Budapest, \ldots

    It's $-30\, ^{\circ}mathrm{C}$.
    I will soon start to
    super-conduct.\\
    30 \textcelsius{} is % relying on textcomp package
    86 \textdegree{}F

    \today{} \LaTeX{} \LaTeXe{} \TeX

    read/write\newline
    read\slash write

    http://www.rich.edu/\~{}bush

    http://www.clever.edu/$\sim$demo

    15113029g@connect.polyu.hk

    daughter-in-law, X-rated\\
    pages 13--67\\
    yes---or no? \\
    $0$, $1$ and $-1$

    \section{This is the second}\label{sec:thisIsMySecondSection}
    A lot of fuker need to learn.

    \ldots{} and here it ends.

    It does not matter whether you
    enter one or several spaces
    after a word.

    An empty line starts a new
    paragraph.

    New \TeX users may miss white spaces after a command.

    Experienced \TeX{} users are \TeX perts, and know how to use whitespaces.

    You can \textsl{lean} on me!

    Please, start a new line
    right here!\newline
    Thank you!

    \include{file1}

    This is an % stupid
    % Better: instructive <----
    example: Supercal%
    ifragilist%
    icexpialidocious
    %
    %    This is another
    %    \begin{comment}
    %        rather stupid,
    %        but helpful
    %    \end{comment}
    %    example for embedding
    %    comments in your document


    % Example 1
    \ldots when Einstein introduced his formula
    \begin{equation}
        e = m \cdot c^2 \; ,
    \end{equation}
    which is at the same time the most widely known
    and the least well understood physical formula.
    % Example 2
    \ldots from which follows Kirchhoff's current law:
    \begin{equation}
        \sum_{k=1}^{n} I_k = 0 \; .
    \end{equation}
    Kirchhoff's voltage law can be derived \ldots
    % Example 3
    \ldots which has several advantages.
    \begin{equation}
        I_D = I_F - I_R
    \end{equation}
    is the core of a very different transistor model. \ldots

    ``Please type `X' ''

    "Please type 'X' "

\end{document}